03 - Analyses coding

### 2022-06-16 data/osf/norming/README.Rmd

- The `images/` directory contains the re-colored images used in the norming study.
- The `results/` directory holds an aggregated `tipicality.csv` file with the typicality ratings of each image/object for each participant.

The `tipicality.csv` file has the following columns:

- `prolific id`: The participant/trial id.
- `object`: The name of the object represented in the image.
- `typicality`: The typicality rating (numeric, `1-100`, `1` = most atypical, `100` = most typical).
- `colour`: The color of the object in the image.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "norming") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

>>>>

- The `images/` directory contains the re-colored images used in the norming study.
- The `ratings/` directory holds an aggregated `ratings.csv` file with the typicality ratings of each image/object for each participant.

# Ratings

The `ratings.csv` file represents the raw data collected from the norming experiment and has the following columns:

- `subject_id`: The participant/trial id.
- `object`: The name of the object illustrated in the image.
- `typicality`: The typicality rating (numeric, `1-100`, `1` = most atypical, `100` = most typical).
- `colour`: The color of the object in the image.
- `object_en`: The english translation of `object`
- `colour_en`: The english translation of `colour`

The `ratings_summary.csv` represents the aggregated typicality ratings across combinations of object and color.
The file has the following columns:

- `object`: The name of the object illustrated in the image.
- `colour`: The color of the object in the image.
- `object_en`: The english translation of `object`.
- `colour_en`: The english translation of `colour`.
- `typ_mean`: The mean typicality rating.
- `typ_sd`: The standard deviation of the typicality ratings .
- `typ_median`: The median typicality rating.

### 2022-06-16 scripts/r/03_analyses_coding.Rmd

Now we get only those components that are assigned to you. Tell me who you are when prompt.

@@

And now we download the components in `data/analyses/`

@@

@@

Here's some code that does that for you.

@@

# Get estimated from refitted models

We first download all the refitted models .rds files from the OSF

@@

A few helpers.

```{r helpers}
# Plotting theme because Im extra
clean_theme <- function(...) {
  list(
    theme_minimal(), 
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
  )
}

@@

```{r load-models}
msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
```

```{r effect-table}
# Simple pandoc table of the models, estimates, se, etc.
msa_models %>% 
  unnest(sum) %>% 
  select(-model) %>% 
  knitr::kable(format = "pandoc")
```

```{r forest-plot}
# Simple forest plot of the estimates +/- SE
msa_models %>% 
  unnest(sum) %>% 
  mutate(
    typicality_lab = if_else(
      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
    ), 
    mod_name = fct_reorder(mod_name, estimate)
  ) %>% 
  ggplot(aes(x = estimate, y = mod_name)) + 
  geom_vline(xintercept = 0) +
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

>>>>

Now we get only those components that are assigned to you. Tell me who you are when prompted.

@@

And now we download the components in `data/analyses/` (it will take some time!).

@@

# Upload refitted models to OSF

@@

Here's the code that does that for you.

@@

# Download all refitted models

We first download all the refitted models .rds files from the OSF.

@@

# Get estimates from refitted models

Now we can extract the relevant estimates from the refitted models.

A few helper functions.

```{r helpers}
# Plotting theme
clean_theme <- function(...) {
  list(
    theme_minimal(), 
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
  )
}

@@

Load all the models.

```{r load-models}
msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  # because it warns every time that some coef have underscores and its annoying
  suppressWarnings()
```

Simple pandoc table of the models, estimates, se, etc.

```{r effect-table}
msa_models %>% 
  unnest(sum) %>% 
  select(-model) %>% 
  knitr::kable(format = "pandoc")
```

Simple forest plot of the estimates +/- SE

```{r forest-plot}
msa_models %>% 
  unnest(sum) %>% 
  mutate(
    typicality_lab = if_else(
      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
    ), 
    mod_name = fct_reorder(mod_name, estimate)
  ) %>% 
  ggplot(aes(x = estimate, y = mod_name)) + 
  geom_vline(xintercept = 0) +
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```
